Selection Coefficients

### 2021-09-08 graphs_newt_snakes/selection_coefficients.Rmd
I added slim onto the slim file. I also makde a r file to add lines to show how the population size moves throughout the simulation.
added more to reproduction callback to increase the number of offsprings produced. I also made the normal distribution into a pois distribution so that an interger whould be picked. In the selection coefficents r markdown I added a line to calculate the number of interaction in a larger population.
I ran a test to see how many newts would be in a snake's range and added that to the selection coefficents r markdown file. I also made a test python file so that I co

@@

## No Space SLiM Results

next one

>>>>

interaction_rate = 0.05
population_size = 3369
number_of_interaction = population_size*interaction_rate
print(paste0("Now if I pick the interaction rate of ", interaction_rate, " and the number of individuals is ", population_size, ", the number of interactions should be ", number_of_interaction))

@@

## How many newts are near a snake???

I had SLiM print out the amount of newts that were in the range of each newt for 1000 generations. The parameters/msprime file were  "newt_snake/data/both_1000_su_1e-10_nu_1e-10_sue_0.1_nue_0.1_try_this_peter.init.trees"

```{r, how many newts in range}
newts_in_snakes_range <- read.table("~/Desktop/how_many_newts_in_range.txt", header =FALSE)

hist(newts_in_snakes_range$V1, c="darkorchid4", main="Number of Newts Near a Snake", xlab="Number of Newts")
abline(v = mean(newts_in_snakes_range$V1), col = "black", lwd = 2)
```

This purple Loch Ness monster represents the number of newts that resign in a particulars snakes range. It seems the mean is around 4, so there are on average 4 newts in a snakes range. I got these values from this line of slim: i1.nearestNeighborsOfPoint(p1, mPoint, count=1000000), which might be something that I can control (change in the future?).

## No Space SLiM

Trying to make a realistic interaction between newts and snakes without space as a factor.
I am also trying to make reproduction more realistic.

### Peters thoughts on the factors that will make the interaction more realstic

Suppose that they all live in a rectangular valley measuring **W** x **L** meters square. Each snake moves around in a range of area **As**. Say there are **Ns** snakes and **Nn** newts.

1. How many newts on average are there in the range of a given snake? **As** * **Nn**/**W*****L**
2. What proportion of newts are within the range of a given snake? (**As** * **Nn**/**W*****L**)**Nn**
3. Suppose that when Nn == Ns we'd like each snake to encounter one newt on average every y years. What proportion of the newts within the snake's range should each snake encounter? ((**As** * **Nn**/**W*****L**)**Nn**)/**y**
